---
title: "HCAMP Lower Extremity"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )


biif <- import(here("data", "BIIF.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))

oia <- import(here("data", "OIA.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))


kif <- import(here("data", "KIF.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))


mil <- import(here("data", "MIL.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))

str(kif)
str(mil)
str(biif)
str(oia)


all_leagues <- bind_rows(biif, oia, kif, mil, .id = "dataset")


  

mean_2 <- function(x) {
  z <- na.omit(x)
  sum(z) / length(z)
}

my_mean <- function(x) {
  mean(x[x >= 0], na.rm = TRUE)
}

mean_2(all_leagues$days_missed)
my_mean(all_leagues$days_missed)


#demo code from Daniel 

#header <- readxl::read_xlsx(here::here("data", "demo_data.xlsx"),
                            #n_max = 1)

#columns <- readxl::read_xlsx(here::here("data", "demo_data.xlsx"),
                             #skip = 1, n_max = 1)

#tbl <- tibble(spanner = names(header),
              #col = names(columns)) %>% 
  #mutate(spanner = gsub("\\.{3}\\d\\d?", NA_character_, spanner),
         #col = gsub("\\.{3}\\d\\d?", "", col)) %>% 
  #fill(spanner)

#new_names <- apply(tbl, 1, function(x) paste0(x[!is.na(x)], collapse = "_"))

#demo_data <- readxl::read_xlsx(here::here("data", "demo_data.xlsx"))

#names(demo_data) <- new_names

#demo_data %>% 
  #janitor::clean_names()
```

```{r, include=FALSE}
create_react <- function(df, var) {
    df %>% 
      summarize(Mean = mean({{var}}),
                SD = sd({{var}}),
                Min = min({{var}}),
                Max = max({{var}}),
                Total = length({{var}})) %>% 
      mutate_if(is.numeric, round, 2) %>% 
      reactable(columns = list(
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE))
      ))
}

```

```{r, include=FALSE}
all_leagues$gender

all_leagues <- all_leagues %>% 
  mutate(gender = recode(gender,
                         `F` = "Female",
                         `M` = "Male"),
         level = recode(level,
                        `JV` = "Junior Varsity"))


all_leagues %>% 
  count(injury)

all_leagues %>% 
  count(days_missed)

all_leagues$days_missed

mean_2(all_leagues$days_missed)

#days missed by injury 

injury_type <- all_leagues %>% 
  group_by(injury) %>% 
  summarize(mean(days_missed))

all_leagues$injury

all_leagues %>% 
  count(injury)
```

```{r, include=FALSE}
injury_total <- all_leagues %>% 
  count(injury) %>% 
  arrange(desc(n))
```

```{r, include=FALSE}
# filter data set for people with concussion as first injury

multiple_injury <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(injury, onset),
    names_glue = "{.value}_{number}"
  )

# filter to concussion as first injury 

concussion_first_injury <- multiple_injury %>% 
  filter(injury_1 == "Head Concussion") %>% 
  select(c(1:3)) %>% 
  na.omit()

#filter injury onset dates 

multiple_injury_onset_dates <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(onset),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_1 <- left_join(concussion_first_injury, multiple_injury_onset_dates)

# next things to widen are days missed, repeated concussion for injury 1, sport, and age

# then need to combine age, gender, name, league, and school

#days missed
days_missed <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(days_missed),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_days_missed <- left_join(join_1, days_missed)


#repeated concussion
repeat_concussion <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(repeated_concussion),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:2)) 

repeat_concussion %>% 
  count(repeated_concussion_1)

#I don't think repeat concussion variable will be helpful but keep code and df to show them in meeting 

#school year
school_year <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(school_year),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_school_year <- left_join(join_days_missed, school_year)

# last name
last_name <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(last_name),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_last_name <- left_join(join_school_year, last_name)

#first name
first_name <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(first_name),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_first_name <- left_join(join_last_name, first_name)

#school

school <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(school),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_school <- left_join(join_first_name, school)


#league

league <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(league),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_league <- left_join(join_school, league)

#gender
gender <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(gender),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_gender <- left_join(join_league, gender)

#age
age <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(age),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()


join_age <- left_join(join_gender, age)

#sport
sport <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(sport),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_sport <- left_join(join_age, sport)

#level 
level <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(level),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_level <- left_join(join_sport, level)

join_level$onset_1 <- as.Date(join_level$onset_1, format = "%m/%d/%Y")
join_level$onset_2 <- as.Date(join_level$onset_2, format = "%m/%d/%Y")

#final sims data set
sims_concussion_first_injury_data <- join_level %>% 
  select(1, 10, 12, 18, 20, 21, 14, 15, 16, 22, 23, 24, 25, 8, 9, 2, 3, 4, 5, 6, 7) %>% 
  rename(last_name = last_name_1,
         first_name = first_name_1,
         gender = gender_1,
         league = league_1) %>% 
  mutate(days_between_injury = onset_2 - onset_1) %>% 
  filter(days_between_injury >= 0 & days_between_injury <= 365) %>% 
  filter(age_1 >= 12 & age_1 <= 18,
         age_2 >= 12 & age_2 <= 18)

sims_concussion_first_injury_le_second_injury <- sims_concussion_first_injury_data %>% 
  filter(injury_2 == "Ankle Achilles Inflammation" |
           injury_2 == "Ankle Achilles Tendon Contusion" |
           injury_2 == "Ankle Achilles Tendon Strain" |
           injury_2 == "Ankle Achilles Tendon Strain 1 Deg" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain 1 Deg" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain 2 Deg" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain 3 Deg" |
           injury_2 == "Ankle Anterior Tibialis Strain" |
           injury_2 == "Ankle Anterior Tibio-Fibular Sprain 1 Deg" |
           injury_2 == "Ankle Anterior Tibio-Fibular Sprain 2 Deg" |
           injury_2 == "Ankle Calcaneofibular Ligament Sprain" |
           injury_2 == "Ankle Contusion/Lateral-Posterior Malleolus" |
           injury_2 == "Ankle Deltoid Ligament Sprain 1 Deg" |
           injury_2 == "Ankle Dislocation" |
           injury_2 == "Ankle Fibular Collateral Ligament Sprain 1 Deg" |
           injury_2 == "Ankle Fracture (non-specific" |
           injury_2 == "Ankle Lateral Sprain" |
           injury_2 == "Ankle Lateral Sprain 1 Deg" |
           injury_2 == "Ankle Lateral Sprain 2 Deg" |
           injury_2 == "Ankle Lateral Sprain 3 Deg" |
           injury_2 == "Ankle Medial Sprain" |
           injury_2 == "Ankle Peroneal Muscle Strain" |
           injury_2 == "Ankle Peroneal Muscle Strain 3 Deg" |
           injury_2 == "Ankle Posterior Tibio-Fibular Sprain" |
           injury_2 == "Ankle Sprain (non-specific)" |
           injury_2 == "Ankle Sprain 1 Deg (non-specific)" |
           injury_2 == "Anterior Tibial Stress Syndrome" |
           injury_2 == "Fibula Achilles Tendon Contusion" |
           injury_2 == "Fibula Bony Contusion/Distal" |
           injury_2 == "Fibula Fracture/Distal" |
           injury_2 == "Fibula Fracture/Non-specific" |
           injury_2 == "Fibula Gastrocnemius Contusion" |
           injury_2 == "Fibula Gastrocnemius Cramps" |
           injury_2 == "Fibula Gastrocnemius Strain 1 Deg" |
           injury_2 == "Fibula Lower Leg Strain/Posterior" |
           injury_2 == "Fibula Plantaris Strain 1 Deg" |
           injury_2 == "Foot 4th Tarsometatarsal Sprain" |
           injury_2 == "Foot 5th Metatarsal Contusion" |
           injury_2 == "Foot Arch Sprain/Traumatic 3 Deg" |
           injury_2 == "Foot Contusion" |
           injury_2 == "Foot Exterior Digitorum Brevis Strain" |
           injury_2 == "Foot Fracture/5th Metatarsal/Base" |
           injury_2 == "Foot Friction Blister" |
           injury_2 == "Foot Lis-Franc Sprain" |
           injury_2 == "Foot Metatarsal Contusion" |
           injury_2 == "Foot Peroneal Tendinitis" |
           injury_2 == "Foot Plantar Fascitis Chronic" |
           injury_2 == "Foot Puncture Wound" |
           injury_2 == "Foot Sprain (non-specific)" |
           injury_2 == "Great Toe Contusion" |
           injury_2 == "Great Toe Flexor Hallicus Longus Strain" |
           injury_2 == "Great Toe Fracture (non-specific)" | 
           injury_2 == "Great Toe I-P Sprain" |
           injury_2 == "Great Toe M-P Sprain 1 Deg/Turf Toe" |
           injury_2 == "Great Toe M-P Sprain/Turf Toe" |
           injury_2 == "Great Toe Nail Subungual Hematoma" |
           injury_2 == "Groin Adductor Longus/Proximal 1 Deg" |
           injury_2 == "Groin Adductor Strain/Proximal" |
           injury_2 == "Groin Adductor Strain/Proximal 2 Deg" |
           injury_2 == "Groin Hamstring Strain/Medial Proximal" |
           injury_2 == "Groin Muscle Strain (non-specific)" |
           injury_2 == "Groin Pubalgia" |
           injury_2 == "Heel Fracture/Non-specific" |
           injury_2 == "Hip Abductor Strain 1 Deg" |
           injury_2 == "Hip Contusion" |
           injury_2 == "Hip Flexor Strain" |
           injury_2 == "Hip Gluteus Maximus Strain" |
           injury_2 == "Hip Iliopectineal Bursitis" |
           injury_2 == "Hip Snapping" |
           injury_2 == "Hip, general trauma" |
           injury_2 == "Knee Abrasion" |
           injury_2 == "Knee Anserine Bursitis" |
           injury_2 == "Knee Anterior Cruciate Sprain" |
           injury_2 == "Knee Anterior Cruciate Sprain 3 Deg" |
           injury_2 == "Knee Anterior Inflammation" |
           injury_2 == "Knee Anterior-Medial Capsule Sprain 1 Deg" |
           injury_2 == "Knee Bursitis" |
           injury_2 == "Knee Chondromalacia" | 
           injury_2 == "Knee Contusion" |
           injury_2 == "Knee General Stress" |
           injury_2 == "Knee Hyperextension Sprain" |
           injury_2 == "Knee Hyperflexion Sprain" |
           injury_2 == "Knee Ilio-Tibial Band Syndrome (ITBS)" |
           injury_2 == "Knee Inflammation/Scar Tissue" |
           injury_2 == "Knee Lateral Capsule Sprain 1 Deg" |
           injury_2 == "Knee Lateral Collateral Sprain" |
           injury_2 == "Knee Lateral Collateral Sprain 2 Dg" |
           injury_2 == "Knee Lateral Hamstring Strain/Distal" |
           injury_2 == "Knee Medial Capsule Sprain" | 
           injury_2 == "Knee Medial Collateral Sprain" | 
           injury_2 == "Knee Medial Collateral Sprain 1 Deg" | 
           injury_2 == "Knee Medial Collateral Sprain 2 Deg" | 
           injury_2 == "Knee Medial Hamstrng Strain/Distal" | 
           injury_2 == "Knee Posterior Cruciate Sprain 3 Dg"| 
           injury_2 == "Knee Posterior-Medial Capsule Sprain" | 
           injury_2 == "Knee Quadriceps Strain/Distal 2 Deg" | 
           injury_2 == "Knee sprain" | 
           injury_2 == "Knee Sprain (non-specific)" | 
           injury_2 == "Knee Tibial Plateau Contusion" |
           injury_2 == "Knee, musculo-skeletal" | 
           injury_2 == "Meniscus Injury" |
           injury_2 == "Meniscus Medial Tear" | 
           injury_2 == "Patella Contusion" | 
           injury_2 == "Patella Dislocation/Acute - Lateral" | 
           injury_2 == "Patella Femoral Syndrome" |
           injury_2 == "Patella Prepatellar Bursa Contusion" |
           injury_2 == "Patella Subluxation/Acute - Lateral" |
           injury_2 == "Patella Subluxation/Acute - Medial" |
           injury_2 == "Patella Tendinitis (Chronic)" | 
           injury_2 == "Thigh Hamstring Strain/Medial Belly" | 
           injury_2 == "Thigh Lateral Contusion" | 
           injury_2 == "Thigh Quads Strain/Belly" | 
           injury_2 == "Thigh Quads Strain/Belly 1 Deg" | 
           injury_2 == "Thigh Rectus Femoris Contusion" |
           injury_2 == "Thigh Rectus Femoris Strain 1 Deg" |
           injury_2 == "Thigh Vastus Medialis Contusion" |
           injury_2 == "Tibia Bony Contusion" |
           injury_2 == "Tibia Bony Contusion Distal" |
           injury_2 == "Tibia Fracture/Distal/Avulsion" |
           injury_2 == "Tibia Medial Stress Syndrome" |
           injury_2 == "Tibia Osgood/Schlatter's Syndrome" |
           injury_2 == "Tibia Shin Splints" |
           injury_2 == "Tibia/shin sprain" |
           injury_2 == "Toe 5th M-P Joint Sprain")
           

#code above filters partiicpants whose second non-concussion injuries occured within one year of concussion

#when code first ran - total was 1137 individuals
#filter individuals days_between_injury >= 0 - total reduced to 1107 individuals
#filter individuals days_between_injury <= 365 - total reduced to 678
#filter individuals with lower extremity injuries to new data frame - total reduced to 238 individuals
# total reduced to 233 when age range restricted to 12-18 

#export sims data with no names

sims_data_1 <- sims_concussion_first_injury_data %>% 
  select(-last_name, -first_name)

sims_data_2 <- sims_concussion_first_injury_le_second_injury %>% 
  select(-last_name, -first_name)

library(writexl)

write_xlsx(sims_data_1, "sims_data_1.xlsx")

write_xlsx(sims_data_2, "sims_data_2.xlsx")


```

```{r, include=FALSE}
#loading up impact data to match post-injury 1 IMPACT scores

files <- dir_ls(here::here("data"), glob = "*.csv")

d <- map_df(files, read_csv, .id = "file",
                 col_types = cols(.default = "c")) %>% 
  modify(~parse_guess(.x)) %>% 
  janitor::clean_names() %>% 
  mutate(year = parse_number(file)) %>% 
  mutate(year = as.factor(year))

d <- d %>% 
  mutate(first_name = str_to_title(first_name),
         last_name = str_to_title(last_name))

impact_variables <- d %>% 
  select(passport_id,
         first_name, 
         last_name, 
         test_type,
         test_date,
         user_memory_composite_score_verbal,
         user_memory_composite_score_visual,
         user_visual_motor_composite_score,
         user_impulse_control_composite_score,
         user_reaction_time_composite_score) %>% 
  rename(verbal_memory = user_memory_composite_score_verbal,
         visual_memory = user_memory_composite_score_visual,
         visual_motor = user_visual_motor_composite_score,
         impulse_control = user_impulse_control_composite_score,
         reaction_time = user_reaction_time_composite_score) %>% 
  filter(test_type == "Post-Injury 1")

str(impact_variables)

impact_variables %>% 
  count(passport_id)

impact_variables$test_date <- as.Date(impact_variables$test_date, format = "%m/%d/%Y")

sims_impact_data <- left_join(sims_concussion_first_injury_data, impact_variables) %>% 
  na.omit() %>% 
  select(-passport_id, -test_type) %>% 
  mutate(days_between_injury_test_date = test_date - onset_1) %>% 
  filter(days_between_injury_test_date >= 0 & days_between_injury_test_date <= 100)

#when data sets first joined, there were 907 total observations - 229 than sims only data set. 
#missing values removed leaving data set with 458 observations
#days between injury 1 onset date filtered to be greater than or equal to 0 days and less than or equal to 100 days leaving 328 observations 

sims_impact_data <- sims_impact_data %>% 
  select(c(1:23, 29, 24:28))

sims_impact_data_all_injuries <- sims_impact_data %>% 
  select(-last_name, -first_name)

write_xlsx(sims_impact_data_all_injuries,"sims_impact_data_all_injuries.xlsx")

sims_impact_data_le_injury_only <- left_join(sims_concussion_first_injury_le_second_injury,
                                             impact_variables) %>% 
  na.omit() %>% 
  select(-passport_id, -test_type) %>% 
  mutate(days_between_injury_test_date = test_date - onset_1) %>% 
  filter(days_between_injury_test_date >= 0 & days_between_injury_test_date <= 100)

write_xlsx(sims_impact_data_le_injury_only, "sims_impact_data_le_injury_only.xlsx")

#with lower injuries only, combined with impact, there are 106 observations - ages filtered to be 12-18

  
```

# Data Background {.tabset .tabset-fade .tabset-pills}

Tables display data from sample 238 individuals from Sims data set that sustained a lower extremity injury within 1 year of sustaining a concussion. To include more data, the information below does not contain information from the merged IMPACT data sample. 

## Gender 

```{r, include=TRUE}
gender_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(gender) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )

```

```{r, include=TRUE}
gender_total_tbl
```

## Age at Concussion

```{r, include=FALSE}
concussion_age_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(age_1) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      age_1 = colDef(name = "Age"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )


```

```{r, include=TRUE}
concussion_age_total_tbl
```

## Age at Second Injury

```{r, include=FALSE}
second_age_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(age_2) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      age_2 = colDef(name = "Age"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )


```

```{r, include=TRUE}
second_age_total_tbl
```

## League

```{r, include=FALSE}
league_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(league) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      league = colDef(name = "League"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
league_total_tbl
```

## School 

```{r, include=FALSE}
school_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(league, school_2) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      league = colDef(name = "League"),
      school_2 = colDef(name = "School"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
school_total_tbl
```

## Sport Played Concussion Injury 

```{r, include=FALSE}
sport_1_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(sport_1) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      sport_1 = colDef(name = "Sport"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
sport_1_total_tbl
```

## Sport Level Concussion Injury 

```{r, include=FALSE}
level_1_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(level_1) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      level_1 = colDef(name = "Level"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
level_1_total_tbl
```

## Sport Played Lower Extremity Injury 

```{r, include=FALSE}
sport_2_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(sport_2) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      sport_2 = colDef(name = "Sport"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
sport_2_total_tbl
```

## Sport Level Lower Extremity Injury 

```{r, include=FALSE}
level_2_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(level_2) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      level_2 = colDef(name = "Level"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
level_2_total_tbl
```

# Second Injury Frequency 

Table reflects 238 individuals from Sims data set with a diagnosed lower extremity injury following a concussion. 

```{r, include=FALSE}
head(sims_concussion_first_injury_le_second_injury)

sims_concussion_first_injury_le_second_injury %>% 
  count(injury_2)

injury_2_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(injury_2) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      injury_2 = colDef(name = "Injury"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

```

```{r, include=TRUE}
injury_2_tbl
```

# Duration of Time Between Concussion and Lower Extremity Injury {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
gender_time_between_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(gender) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>%
  filter(gender == "Female" |
         gender == "Male") %>% 
  mutate(mean = as.numeric(mean),
         sd = as.numeric(sd),
         min = as.numeric(min),
         max = as.numeric(max),
         total = as.numeric(total)) %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )


```

## Gender {.tabset .tabset-fade .tabset-pills}

### Summary Table

Descriptive statistics of time between concussion and lower extremity injury by gender

```{r, include=TRUE}
gender_time_between_tbl
```

### Box Plot

```{r, include=FALSE}
gender_tee <- sims_concussion_first_injury_le_second_injury %>% 
  filter(gender == "Female" |
           gender == "Male")

bxp <- ggboxplot(
  gender_tee, x = "gender", y = "days_between_injury", 
  ylab = "Number of Days", xlab = "Gender", add = "jitter",
  title = "Days Between Injuries"
  )

bxp +
  stat_compare_means(method = "t.test", hjust = -0.2)


gender_bxp <- ggplot(gender_tee, aes(gender, days_between_injury, color = gender)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Between Injuries") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
gender_bxp
```

### *T*-Test Results

```{r, include=FALSE}
gender_tee <- gender_tee %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

gender_tee_results <- gender_tee %>% 
  t_test(days_between_injury ~ gender) %>% 
  add_significance()

gender_tee_results
```

```{r, include=TRUE}
gender_tee_results 
```

## Age {.tabset .tabset-fade .tabset-pills}

### Age Difference Distribution

To create plot, a new variable was created `age_difference` calculated as the difference between injury_2 age and injury_1 age. All differences are less than one year. The distribution is not normal with higher distribution at both tails. 

```{r, include=FALSE}
age_diff <- sims_concussion_first_injury_le_second_injury %>% 
  mutate(age_difference = age_2 - age_1)

hist(age_diff$age_difference)

age_diff_plot <- ggplot(age_diff, aes(age_difference)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  labs(x = "Age Difference (Years)",
       y = "Number of Individuals",
       title = "Age Difference in Years between Two Injuries",
       caption = "All injuries less than one year apart")
```

```{r, include=TRUE}
age_diff_plot
```

### Age 1 Total Distribution

```{r, include=TRUE}
ggplot(age_diff, aes(age_1)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 50) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at First Injury")

```

### Age 1 Distribution League

```{r, include=TRUE}
ggplot(age_diff, aes(age_1)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  facet_wrap(~league) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at First Injury")
```

### Age 1 Distribution Gender

```{r, include=TRUE}
ggplot(age_diff, aes(age_1)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~gender) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at First Injury")
```


### Age 2 Total Distribution

```{r, include=TRUE}
ggplot(age_diff, aes(age_2)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 50) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at Second Injury")

```

### Age 2 Distribution League

```{r, include=TRUE}
ggplot(age_diff, aes(age_2)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  facet_wrap(~league) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at Second Injury")
```

### Age 2 Distribution Gender

```{r, include=TRUE}
ggplot(age_diff, aes(age_2)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~gender) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at Second Injury")
```

```{r, include=FALSE}
age_diff <- age_diff %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

age_diff_mod <- lm(days_between_injury ~ age_2, data = age_diff)

summary(age_diff_mod)
```

### Age Model 

To produce the model, I calculated the relationship between the age at second injury and the days between injuries. There appears to be a significant relationship, although the model only accounts for 5% of the variance. Overall, there is a 31.339 unit increase in the days between injury for every unit increase in the age at time of 2nd injury. 

```{r, include=TRUE}
summary(age_diff_mod)
```

## Sport {.tabset .tabset-fade .tabset-pills}

This section primarily explores the time between injuries for Football and Women's Soccer as those are the two most common sports at time of concussion and lower extremity injury. 

### Descriptive Statistics

Table displayed statistics of the number of days between injuries for individuals who sustained their injuries playing football or women's soccer.

```{r, include=FALSE}
sport_time_between <- sims_concussion_first_injury_le_second_injury %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

spt_tbl <- sport_time_between %>% 
  group_by(sport_1, sport_2) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>% 
  reactable(
    columns = list(
      sport_1 = colDef(name = "Sport 1"),
      sport_2 = colDef(name = "Sport 2"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
spt_tbl
```

### Sport 2 Injury Type

Table displays the number of lower extremity injuries for individuals who played football and women's soccer. 

```{r, include=FALSE}
spt_2_tbl <- sport_time_between %>% 
  group_by(sport_2, injury_2) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      sport_2 = colDef(name = "Sport"),
      injury_2 = colDef(name = "Injury"),
      total = colDef(name = "Total",
                     format = colFormat(suffix = " injuries"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
spt_2_tbl
```

### Box Plot

```{r, include=FALSE}
sport_tee <- sims_concussion_first_injury_le_second_injury %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))


sport_bxp <- ggboxplot(
  sport_tee, x = "sport_2", y = "days_between_injury", 
  ylab = "Number of Days", xlab = "Sport", add = "jitter",
  title = "Days Between Injuries"
  )

sport_bxp +
  stat_compare_means(method = "t.test", hjust = -0.2)


sport_bxp_2 <- ggplot(sport_tee, aes(sport_2, days_between_injury, color = sport_2)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Between Injuries",
       caption = "Sport at time of 2nd injury") +
  stat_compare_means(method = "t.test", hjust = -0.2)

```

```{r, include=TRUE}
sport_bxp_2
```

### *T*-Test Results

```{r, include=FALSE}
sport_tee_results <- sport_tee %>% 
  t_test(days_between_injury ~ sport_2) %>% 
  add_significance()

sport_tee_results
```

```{r, include=TRUE}
sport_tee_results 
```

## School {.tabset .tabset-fade .tabset-pills}

Schools with 20 or more individuals included. 

### Descriptive Statistics 

Table displays statistics of the number of days between injuries for individuals who attend Kalaheo High School, Maui High School, and Mililani High School.

```{r, include=FALSE}
school_analysis <- sims_concussion_first_injury_le_second_injury %>% 
  filter(school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))


school_tbl <- school_analysis %>% 
  group_by(school_2) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>% 
  reactable(
    columns = list(
      school_2 = colDef(name = "School"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
school_tbl
```

### Boxplot

```{r, include=FALSE}
school_analysis <- sims_concussion_first_injury_le_second_injury %>% 
  filter(school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

sch_plot <- ggboxplot(school_analysis, x = "school_2", y = "days_between_injury", 
          color = "school_2", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Maui High School", "Kalaheo High School", "Mililani High School"),
          ylab = "Number of Days", xlab = "", add = "jitter")


sch_bxp <- ggplot(school_analysis, aes(school_2, days_between_injury, color = school_2)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Between Injuries") +
  stat_compare_means(method = "anova", hjust = -0.2)

```

```{r, include=TRUE}
sch_bxp
```

### Anova 

The difference between the mean number of days between injury across the three high schools is significantly different. Students at Mililani High School, on average, experienced a much longer duration of time between injuries than students at Kalaheo High School and Maui High School.

```{r, include=FALSE}
school_res_aov <- aov(days_between_injury ~ school_2, data = school_analysis)

summary(school_res_aov)
```

```{r, include=TRUE}
summary(school_res_aov)
```

### Pairwise Comparisons 

```{r, include=TRUE}
pairwise.t.test(school_analysis$days_between_injury,
                school_analysis$school_2,
                p.adjust.method = "bonferroni")
```


## Level {.tabset .tabset-fade .tabset-pills}

### Descriptive Statistics 

Table displayed statistics of the number of days between injuries for the sport level at the time of the individuals' lower extremity injury. 

```{r, include=FALSE}
level_analysis <- sims_concussion_first_injury_le_second_injury %>% 
  filter(level_2 == "JV" |
         level_2 == "Varsity") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))


level_tbl <- level_analysis %>% 
  group_by(level_2) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>% 
  reactable(
    columns = list(
      level_2 = colDef(name = "Level"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
level_tbl
```

### Box Plot

```{r, include=FALSE}
level_tee <- sims_concussion_first_injury_le_second_injury %>% 
  filter(level_1 == "Junior Varsity" | level_1 == "Varsity",
         level_2 == "Junior Varsity" | level_2 == "Varsity") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))


level_bxp <- ggplot(level_tee, aes(level_2, days_between_injury, color = level_2)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  labs(x = "",
       y = "Number of Days",
       title = "Days Between Injuries",
       caption = "Level at time of 2nd injury") +
  theme(legend.position = "none") +
  stat_compare_means(method = "t.test", hjust = -0.2)

```

```{r, include=TRUE}
level_bxp
```

### *T*-Test Results

Individuals playing varsity sports at the time of second injury have a significantly different longer duration of time between injuries. 

```{r, include=FALSE}
level_tee_results <- level_tee %>% 
  t_test(days_between_injury ~ level_2) %>% 
  add_significance()
```

```{r, include=TRUE}
level_tee_results 
```

# Days Missed Following Injuries {.tabset .tabset-fade .tabset-pills}

One individual removed from sample because of missing information for days since both injuries reducing sample total to 232 individauls. The number of days missed post-concussion appears to have severe outliers? 

```{r, include=FALSE}

days_missed_data <- sims_concussion_first_injury_le_second_injury %>% 
  rename(days_missed_concussion = days_missed_1,
         days_missed_lower_extremity = days_missed_2) %>% 
  drop_na(days_missed_concussion) %>% 
  drop_na(days_missed_lower_extremity)


days_missed_long <- days_missed_data %>% 
  pivot_longer(
    cols = c(20:21),
    names_to = "injury",
    names_prefix = "days_missed_",
    values_to = "days_missed"
  ) %>% 
  mutate(injury = recode(injury,
                         `lower_extremity` = "lower extremity")) %>% 
  drop_na(days_missed)

days_missed_concussion <- days_missed_data %>% 
  group_by(injury_1) %>% 
  summarize(mean = mean(days_missed_concussion),
            sd = sd(days_missed_concussion),
            min = min(days_missed_concussion),
            max = max(days_missed_concussion),
            total = length(days_missed_concussion)) %>% 
  reactable(
    columns = list(
      injury_1 = colDef(name = "Injury"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE      
    )

days_missed_le <- days_missed_data %>% 
  group_by(injury_2) %>% 
  summarize(mean = mean(days_missed_lower_extremity),
            sd = sd(days_missed_lower_extremity),
            min = min(days_missed_lower_extremity),
            max = max(days_missed_lower_extremity),
            total = length(days_missed_lower_extremity)) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      injury_2 = colDef(name = "Injury"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE      
    )
```

## Descriptive Statistics {.tabset .tabset-fade .tabset-pills}

### Days Missed Following Concussion

```{r, include=TRUE}
days_missed_concussion
```

### Days Missed Following Lower Extremity Injury 

```{r, include=TRUE}
days_missed_le
```

## Days Missed Visualizations {.tabset .tabset-fade .tabset-pills}

### Concussion Total

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_concussion)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Concussion")
```

### Concussion by Gender

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_concussion)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~gender) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Concussion")
```

### Concussion by League

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_concussion)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~league) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Concussion")
```

### Concussion by Level

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_concussion)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~level_1) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Concussion")
```


### Lower Extremity Total

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_lower_extremity)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Lower Extremity Injury")
```

### Lower Extremity by Gender

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_lower_extremity)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~gender) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Lower Extremity Injury")
```

### Lower Extremity by League

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_lower_extremity)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~league) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following Lower Extremity Injury")
```

### Lower Extremity by Level

```{r, include=TRUE}
ggplot(days_missed_data, aes(days_missed_lower_extremity)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~level_2) +
  labs(x = "Number of Days",
       y = "Number of Individuals",
       title = "Days Missed Following lower Extremity Injury")
```

## *T*-Test Across Entire Sample {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
head(days_missed_long)

days_missed_bxp <- ggplot(days_missed_long, aes(injury, days_missed, color = injury)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Injury") +
  theme(legend.position = "none") +
  stat_compare_means(method = "t.test", hjust = -0.2)

days_missed_1 <- days_missed_data$days_missed_concussion
days_missed_2 <- days_missed_data$days_missed_lower_extremity

days_missed_res <- t.test(days_missed_1, days_missed_2, paired = TRUE)

days_missed_res

days_missed_res$p.value
days_missed_res$estimate
days_missed_res$statistic

```

### Boxplot

```{r, include=TRUE}
days_missed_bxp
```

### Results

```{r, include=TRUE}
days_missed_res
```

## Gender {.tabset .tabset-fade .tabset-pills}

### Days Missed Following Concussion

```{r, include=FALSE}

gender_days_missed_concussion <- days_missed_data %>% 
  group_by(gender) %>% 
  summarize(mean = mean(days_missed_concussion),
            sd = sd(days_missed_concussion),
            min = min(days_missed_concussion),
            max = max(days_missed_concussion),
            total = length(days_missed_concussion)) %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE      
    )
```

```{r, include=TRUE}
gender_days_missed_concussion
```

### Days Missed Following Lower Extremity Injury

```{r, include=FALSE}

gender_days_missed_le <- days_missed_data %>% 
  group_by(gender) %>% 
  summarize(mean = mean(days_missed_lower_extremity),
            sd = sd(days_missed_lower_extremity),
            min = min(days_missed_lower_extremity),
            max = max(days_missed_lower_extremity),
            total = length(days_missed_lower_extremity)) %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE      
    )
```

```{r, include=TRUE}
gender_days_missed_le
```

### Concussion Box Plot 

```{r, include=FALSE}

gender_concussion_days_missed_tee <- days_missed_data %>% 
  filter(gender == "Female" |
           gender == "Male")


gender_days_missed_concussion_bxp <- ggplot(gender_concussion_days_missed_tee, aes(gender, days_missed_concussion, color = gender)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Concussion") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
gender_days_missed_concussion_bxp
```

### Concussion *T*-Test Results

```{r, include=FALSE}
gender_days_missed_concussion_tee_results <- gender_concussion_days_missed_tee %>% 
  t_test(days_missed_concussion ~ gender) %>% 
  add_significance()
```

```{r, include=TRUE}
gender_days_missed_concussion_tee_results
```

### Lower Extremity Box Plot 

```{r, include=FALSE}

gender_le_days_missed_tee <- days_missed_data %>% 
  filter(gender == "Female" |
           gender == "Male")


gender_days_missed_le_bxp <- ggplot(gender_le_days_missed_tee, aes(gender, days_missed_lower_extremity, color = gender)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Lower Extremity Injury") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
gender_days_missed_le_bxp
```

### Lower Extremity *T*-Test Results

```{r, include=FALSE}
gender_days_missed_le_tee_results <- gender_le_days_missed_tee %>% 
  t_test(days_missed_lower_extremity ~ gender) %>% 
  add_significance()
```

```{r, include=TRUE}
gender_days_missed_le_tee_results
```

## Age {.tabset .tabset-fade .tabset-pills}

There does not appear to be a strong relationship between age and the number of days missed following either a concussion or lower extremity injury. 

### Concussion

```{r, include=TRUE}
ggplot(days_missed_data, aes(age_1, days_missed_concussion)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Age",
       y = "Number of Days",
       title = "Days Missed Following Concussion Related to Age")

```

### Lower Extremity Injury 

```{r, include=TRUE}
ggplot(days_missed_data, aes(age_2, days_missed_lower_extremity)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Age",
       y = "Number of Days",
       title = "Days Missed Following Lower Extremity Injury Related to Age")

```

## Sport {.tabset .tabset-fade .tabset-pills}

This section primarily explores the number of days missed following injuries for Football and Women's Soccer as those are the two most common sports at time of concussion and lower extremity injury. 

### Days Missed Following Concussion

```{r, include=FALSE}
sport_days_missed <- days_missed_data %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") 

days_missed_spt_tbl <- sport_days_missed %>% 
  group_by(sport_1) %>% 
  summarize(mean = mean(days_missed_concussion),
            sd = sd(days_missed_concussion),
            min = min(days_missed_concussion),
            max = max(days_missed_concussion),
            total = length(days_missed_concussion)) %>% 
  reactable(
    columns = list(
      sport_1 = colDef(name = "Sport"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
days_missed_spt_tbl
```

### Days Missed Following Lower Extremity Injury

```{r, include=FALSE}
days_missed_spt_tbl_2 <- sport_days_missed %>% 
  group_by(sport_2) %>% 
  summarize(mean = mean(days_missed_lower_extremity),
            sd = sd(days_missed_lower_extremity),
            min = min(days_missed_lower_extremity),
            max = max(days_missed_lower_extremity),
            total = length(days_missed_lower_extremity)) %>% 
  reactable(
    columns = list(
      sport_2 = colDef(name = "Sport"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
days_missed_spt_tbl_2
```

### Concussion Box Plot 

```{r, include=FALSE}

sport_concussion_days_missed_tee <- days_missed_data %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") 


sport_days_missed_concussion_bxp <- ggplot(sport_concussion_days_missed_tee, aes(sport_1, days_missed_concussion, color = sport_1)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Concussion") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
sport_days_missed_concussion_bxp
```

### Concussion *T*-Test Results

```{r, include=FALSE}
sport_days_missed_concussion_tee_results <- sport_concussion_days_missed_tee %>% 
  t_test(days_missed_concussion ~ sport_1) %>% 
  add_significance()
```

```{r, include=TRUE}
sport_days_missed_concussion_tee_results
```

### Lower Extremity Box Plot 

```{r, include=FALSE}

sport_le_days_missed_tee <- days_missed_data %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") 


sport_days_missed_le_bxp <- ggplot(sport_le_days_missed_tee, aes(sport_2, days_missed_lower_extremity, color = sport_2)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Lower Extremity Injury") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
sport_days_missed_le_bxp
```

### Lower Extremity *T*-Test Results

```{r, include=FALSE}
sport_days_missed_le_tee_results <- sport_le_days_missed_tee %>% 
  t_test(days_missed_lower_extremity ~ sport_2) %>% 
  add_significance()
```

```{r, include=TRUE}
sport_days_missed_le_tee_results
```


## School {.tabset .tabset-fade .tabset-pills}

Schools with 20 or more individuals included. Tables display statistics of the number of days missed following a concussion for individuals who attend Kalaheo High School, Maui High School, and Mililani High School.

### Days Missed Following Concussion


```{r, include=FALSE}
days_missed_concussion_school_analysis <- days_missed_data %>% 
  filter(school_1 == "Maui High School" |
           school_1 == "Kalaheo High School" |
           school_1 == "Mililani High School",
          school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School") 

days_missed_concussion_school_tbl <- days_missed_concussion_school_analysis %>% 
  group_by(school_1) %>% 
  summarize(mean = mean(days_missed_concussion),
            sd = sd(days_missed_concussion),
            min = min(days_missed_concussion),
            max = max(days_missed_concussion),
            total = length(days_missed_concussion)) %>% 
  reactable(
    columns = list(
      school_1 = colDef(name = "School"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
days_missed_concussion_school_tbl
```


### Days Missed Following Lower Extremity Injury


```{r, include=FALSE}

days_missed_le_school_tbl <- days_missed_concussion_school_analysis %>% 
  group_by(school_2) %>% 
  summarize(mean = mean(days_missed_lower_extremity),
            sd = sd(days_missed_lower_extremity),
            min = min(days_missed_lower_extremity),
            max = max(days_missed_lower_extremity),
            total = length(days_missed_lower_extremity)) %>% 
  reactable(
    columns = list(
      school_2 = colDef(name = "School"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
days_missed_le_school_tbl
```

### Boxplot Concussion

```{r, include=FALSE}
concussion_school_analysis <- days_missed_data %>% 
  filter(school_1 == "Maui High School" |
           school_1 == "Kalaheo High School" |
           school_1 == "Mililani High School",
           school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School")

concussion_sch_bxp <- ggplot(concussion_school_analysis, 
                             aes(school_1, days_missed_concussion, color = school_1)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Concussion") +
  stat_compare_means(method = "anova", hjust = -0.2)
```

```{r, include=TRUE}
concussion_sch_bxp
```

### Anova Concussion

The difference between the mean number of days missed following a concussion across the three high schools is not significantly different. 

```{r, include=FALSE}
concussion_school_res_aov <- aov(days_missed_concussion ~ school_1, data = concussion_school_analysis)

summary(concussion_school_res_aov)
```

```{r, include=TRUE}
summary(concussion_school_res_aov)
```


### Boxplot Lower Extremity Injury

```{r, include=FALSE}
le_school_analysis <- days_missed_data %>% 
  filter(school_1 == "Maui High School" |
           school_1 == "Kalaheo High School" |
           school_1 == "Mililani High School",
           school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School")

le_sch_bxp <- ggplot(concussion_school_analysis, 
                             aes(school_2, days_missed_lower_extremity, color = school_2)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Lower Extremity Injury") +
  stat_compare_means(method = "anova", hjust = -0.2)
```

```{r, include=TRUE}
le_sch_bxp
```

### Anova Lower Extremity Injury

The difference between the mean number of days missed following a lower extremity injury across the three high schools is not significantly different. 

```{r, include=FALSE}
le_school_res_aov <- aov(days_missed_lower_extremity ~ school_2, data = le_school_analysis)

summary(le_school_res_aov)
```

```{r, include=TRUE}
summary(le_school_res_aov)
```


## Level {.tabset .tabset-fade .tabset-pills}

### Days Missed Following Concussion


```{r, include=FALSE}

days_missed_concussion_level_analysis <- days_missed_data %>% 
  mutate(level_1 = recode(level_1,
                          `JV` = "Junior Varsity"),
         level_2 = recode(level_2,
                          `JV` = "Junior Varsity")) %>% 
  filter(level_1 == "Junior Varsity" |
         level_1 == "Varsity",
         level_2 == "Junior Varsity" |
         level_2 == "Varsity")
          

days_missed_concussion_level_tbl <- days_missed_concussion_level_analysis %>% 
  group_by(level_1) %>% 
  summarize(mean = mean(days_missed_concussion),
            sd = sd(days_missed_concussion),
            min = min(days_missed_concussion),
            max = max(days_missed_concussion),
            total = length(days_missed_concussion)) %>% 
  reactable(
    columns = list(
      level_1 = colDef(name = "Level"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
days_missed_concussion_level_tbl
```


### Days Missed Following Lower Extremity Injury


```{r, include=FALSE}

days_missed_le_level_tbl <- days_missed_concussion_level_analysis %>% 
  group_by(level_2) %>% 
  summarize(mean = mean(days_missed_lower_extremity),
            sd = sd(days_missed_lower_extremity),
            min = min(days_missed_lower_extremity),
            max = max(days_missed_lower_extremity),
            total = length(days_missed_lower_extremity)) %>% 
  reactable(
    columns = list(
      level_2 = colDef(name = "Level"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
days_missed_le_level_tbl
```


### Concussion Box Plot 

```{r, include=FALSE}
level_days_missed_concussion_bxp <- ggplot(days_missed_concussion_level_analysis, aes(level_1, days_missed_concussion, color = level_1)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Concussion") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
level_days_missed_concussion_bxp
```

### Concussion *T*-Test Results

```{r, include=FALSE}
level_days_missed_concussion_tee_results <- days_missed_concussion_level_analysis %>% 
  t_test(days_missed_concussion ~ level_1) %>% 
  add_significance()
```

```{r, include=TRUE}
level_days_missed_concussion_tee_results
```

### Lower Extremity Box Plot 

```{r, include=FALSE}
level_days_missed_le_bxp <- ggplot(days_missed_concussion_level_analysis, aes(level_2, days_missed_lower_extremity, color = level_2)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(0.2)) +
  scale_color_OkabeIto() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Number of Days",
       title = "Days Missed Following Lower Extremity Injury") +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
level_days_missed_le_bxp
```

### Concussion *T*-Test Results

Varsity athletes, on average, missed a significantly larger amount of time following a lower extremity injury (*M* = 226.43 days) compared to junior varsity athletes following a lower extremity injury (*M* = 79.56 days).

```{r, include=FALSE}
level_days_missed_le_tee_results <- days_missed_concussion_level_analysis %>% 
  t_test(days_missed_lower_extremity ~ level_2) %>% 
  add_significance()
```

```{r, include=TRUE}
level_days_missed_le_tee_results
```

# Impact Scores  {.tabset .tabset-fade .tabset-pills}

Scores represent sample of individuals ages 12-18 who sustained a lower extremity injury within 1 year of their concussion

## Verbal Memory

```{r, include=TRUE}
create_react(sims_impact_data_le_injury_only, verbal_memory)
```

## Visual Memory

```{r, include=TRUE}
create_react(sims_impact_data_le_injury_only, visual_memory)
```

## Visual Motor

```{r, include=TRUE}
create_react(sims_impact_data_le_injury_only, visual_motor)
```

## Impulse Control

```{r, include=TRUE}
create_react(sims_impact_data_le_injury_only, impulse_control)
```

## Reaction Time

```{r, include=TRUE}
create_react(sims_impact_data_le_injury_only, reaction_time)
```