---
title: "HCAMP Lower Extremity"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )


biif <- import(here("data", "BIIF.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))

oia <- import(here("data", "OIA.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))


kif <- import(here("data", "KIF.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))


mil <- import(here("data", "MIL.xlsx"),
               setclass = "tbl_df") %>% 
  janitor::clean_names() %>% 
  select(c(1:12, 21, 25))

str(kif)
str(mil)
str(biif)
str(oia)


all_leagues <- bind_rows(biif, oia, kif, mil, .id = "dataset")


  

mean_2 <- function(x) {
  z <- na.omit(x)
  sum(z) / length(z)
}


#demo code from Daniel 

#header <- readxl::read_xlsx(here::here("data", "demo_data.xlsx"),
                            #n_max = 1)

#columns <- readxl::read_xlsx(here::here("data", "demo_data.xlsx"),
                             #skip = 1, n_max = 1)

#tbl <- tibble(spanner = names(header),
              #col = names(columns)) %>% 
  #mutate(spanner = gsub("\\.{3}\\d\\d?", NA_character_, spanner),
         #col = gsub("\\.{3}\\d\\d?", "", col)) %>% 
  #fill(spanner)

#new_names <- apply(tbl, 1, function(x) paste0(x[!is.na(x)], collapse = "_"))

#demo_data <- readxl::read_xlsx(here::here("data", "demo_data.xlsx"))

#names(demo_data) <- new_names

#demo_data %>% 
  #janitor::clean_names()
```

```{r, include=FALSE}
create_react <- function(df, var) {
    df %>% 
      summarize(Mean = mean({{var}}),
                SD = sd({{var}}),
                Min = min({{var}}),
                Max = max({{var}}),
                Total = length({{var}})) %>% 
      mutate_if(is.numeric, round, 2) %>% 
      reactable(columns = list(
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE))
      ))
}

```

```{r, include=FALSE}
all_leagues$gender

all_leagues <- all_leagues %>% 
  mutate(gender = recode(gender,
                         `F` = "Female",
                         `M` = "Male"))


all_leagues %>% 
  count(injury)

all_leagues %>% 
  count(days_missed)

all_leagues$days_missed

mean_2(all_leagues$days_missed)

#days missed by injury 

injury_type <- all_leagues %>% 
  group_by(injury) %>% 
  summarize(mean(days_missed))

all_leagues$injury

all_leagues %>% 
  count(injury)
```

```{r, include=FALSE}
injury_total <- all_leagues %>% 
  count(injury) %>% 
  arrange(desc(n))
```

```{r, include=FALSE}
# filter data set for people with concussion as first injury

multiple_injury <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(injury, onset),
    names_glue = "{.value}_{number}"
  )

# filter to concussion as first injury 

concussion_first_injury <- multiple_injury %>% 
  filter(injury_1 == "Head Concussion") %>% 
  select(c(1:3)) %>% 
  na.omit()

#filter injury onset dates 

multiple_injury_onset_dates <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(onset),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_1 <- left_join(concussion_first_injury, multiple_injury_onset_dates)

# next things to widen are days missed, repeated concussion for injury 1, sport, and age

# then need to combine age, gender, name, league, and school

#days missed
days_missed <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(days_missed),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_days_missed <- left_join(join_1, days_missed)


#repeated concussion
repeat_concussion <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(repeated_concussion),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:2)) 

repeat_concussion %>% 
  count(repeated_concussion_1)

#I don't think repeat concussion variable will be helpful but keep code and df to show them in meeting 

#school year
school_year <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(school_year),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_school_year <- left_join(join_days_missed, school_year)

# last name
last_name <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(last_name),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_last_name <- left_join(join_school_year, last_name)

#first name
first_name <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(first_name),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_first_name <- left_join(join_last_name, first_name)

#school

school <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(school),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_school <- left_join(join_first_name, school)


#league

league <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(league),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_league <- left_join(join_school, league)

#gender
gender <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(gender),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_gender <- left_join(join_league, gender)

#age
age <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(age),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()


join_age <- left_join(join_gender, age)

#sport
sport <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(sport),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_sport <- left_join(join_age, sport)

#level 
level <- all_leagues %>% 
  group_by(student_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = student_id, 
    names_from = number,
    values_from = c(level),
    names_glue = "{.value}_{number}"
  ) %>% 
  select(c(1:3)) %>% 
  na.omit()

join_level <- left_join(join_sport, level)

join_level$onset_1 <- as.Date(join_level$onset_1, format = "%m/%d/%Y")
join_level$onset_2 <- as.Date(join_level$onset_2, format = "%m/%d/%Y")

#final sims data set
sims_concussion_first_injury_data <- join_level %>% 
  select(1, 10, 12, 18, 20, 21, 14, 15, 16, 22, 23, 24, 25, 8, 9, 2, 3, 4, 5, 6, 7) %>% 
  rename(last_name = last_name_1,
         first_name = first_name_1,
         gender = gender_1,
         league = league_1) %>% 
  mutate(days_between_injury = onset_2 - onset_1) %>% 
  filter(days_between_injury >= 0 & days_between_injury <= 365) %>% 
  filter(age_1 >= 12 & age_1 <= 18,
         age_2 >= 12 & age_2 <= 18)

sims_concussion_first_injury_le_second_injury <- sims_concussion_first_injury_data %>% 
  filter(injury_2 == "Ankle Achilles Inflammation" |
           injury_2 == "Ankle Achilles Tendon Contusion" |
           injury_2 == "Ankle Achilles Tendon Strain" |
           injury_2 == "Ankle Achilles Tendon Strain 1 Deg" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain 1 Deg" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain 2 Deg" |
           injury_2 == "Ankle Anterior Talo-Fibular Sprain 3 Deg" |
           injury_2 == "Ankle Anterior Tibialis Strain" |
           injury_2 == "Ankle Anterior Tibio-Fibular Sprain 1 Deg" |
           injury_2 == "Ankle Anterior Tibio-Fibular Sprain 2 Deg" |
           injury_2 == "Ankle Calcaneofibular Ligament Sprain" |
           injury_2 == "Ankle Contusion/Lateral-Posterior Malleolus" |
           injury_2 == "Ankle Deltoid Ligament Sprain 1 Deg" |
           injury_2 == "Ankle Dislocation" |
           injury_2 == "Ankle Fibular Collateral Ligament Sprain 1 Deg" |
           injury_2 == "Ankle Fracture (non-specific" |
           injury_2 == "Ankle Lateral Sprain" |
           injury_2 == "Ankle Lateral Sprain 1 Deg" |
           injury_2 == "Ankle Lateral Sprain 2 Deg" |
           injury_2 == "Ankle Lateral Sprain 3 Deg" |
           injury_2 == "Ankle Medial Sprain" |
           injury_2 == "Ankle Peroneal Muscle Strain" |
           injury_2 == "Ankle Peroneal Muscle Strain 3 Deg" |
           injury_2 == "Ankle Posterior Tibio-Fibular Sprain" |
           injury_2 == "Ankle Sprain (non-specific)" |
           injury_2 == "Ankle Sprain 1 Deg (non-specific)" |
           injury_2 == "Anterior Tibial Stress Syndrome" |
           injury_2 == "Fibula Achilles Tendon Contusion" |
           injury_2 == "Fibula Bony Contusion/Distal" |
           injury_2 == "Fibula Fracture/Distal" |
           injury_2 == "Fibula Fracture/Non-specific" |
           injury_2 == "Fibula Gastrocnemius Contusion" |
           injury_2 == "Fibula Gastrocnemius Cramps" |
           injury_2 == "Fibula Gastrocnemius Strain 1 Deg" |
           injury_2 == "Fibula Lower Leg Strain/Posterior" |
           injury_2 == "Fibula Plantaris Strain 1 Deg" |
           injury_2 == "Foot 4th Tarsometatarsal Sprain" |
           injury_2 == "Foot 5th Metatarsal Contusion" |
           injury_2 == "Foot Arch Sprain/Traumatic 3 Deg" |
           injury_2 == "Foot Contusion" |
           injury_2 == "Foot Exterior Digitorum Brevis Strain" |
           injury_2 == "Foot Fracture/5th Metatarsal/Base" |
           injury_2 == "Foot Friction Blister" |
           injury_2 == "Foot Lis-Franc Sprain" |
           injury_2 == "Foot Metatarsal Contusion" |
           injury_2 == "Foot Peroneal Tendinitis" |
           injury_2 == "Foot Plantar Fascitis Chronic" |
           injury_2 == "Foot Puncture Wound" |
           injury_2 == "Foot Sprain (non-specific)" |
           injury_2 == "Great Toe Contusion" |
           injury_2 == "Great Toe Flexor Hallicus Longus Strain" |
           injury_2 == "Great Toe Fracture (non-specific)" | 
           injury_2 == "Great Toe I-P Sprain" |
           injury_2 == "Great Toe M-P Sprain 1 Deg/Turf Toe" |
           injury_2 == "Great Toe M-P Sprain/Turf Toe" |
           injury_2 == "Great Toe Nail Subungual Hematoma" |
           injury_2 == "Groin Adductor Longus/Proximal 1 Deg" |
           injury_2 == "Groin Adductor Strain/Proximal" |
           injury_2 == "Groin Adductor Strain/Proximal 2 Deg" |
           injury_2 == "Groin Hamstring Strain/Medial Proximal" |
           injury_2 == "Groin Muscle Strain (non-specific)" |
           injury_2 == "Groin Pubalgia" |
           injury_2 == "Heel Fracture/Non-specific" |
           injury_2 == "Hip Abductor Strain 1 Deg" |
           injury_2 == "Hip Contusion" |
           injury_2 == "Hip Flexor Strain" |
           injury_2 == "Hip Gluteus Maximus Strain" |
           injury_2 == "Hip Iliopectineal Bursitis" |
           injury_2 == "Hip Snapping" |
           injury_2 == "Hip, general trauma" |
           injury_2 == "Knee Abrasion" |
           injury_2 == "Knee Anserine Bursitis" |
           injury_2 == "Knee Anterior Cruciate Sprain" |
           injury_2 == "Knee Anterior Cruciate Sprain 3 Deg" |
           injury_2 == "Knee Anterior Inflammation" |
           injury_2 == "Knee Anterior-Medial Capsule Sprain 1 Deg" |
           injury_2 == "Knee Bursitis" |
           injury_2 == "Knee Chondromalacia" | 
           injury_2 == "Knee Contusion" |
           injury_2 == "Knee General Stress" |
           injury_2 == "Knee Hyperextension Sprain" |
           injury_2 == "Knee Hyperflexion Sprain" |
           injury_2 == "Knee Ilio-Tibial Band Syndrome (ITBS)" |
           injury_2 == "Knee Inflammation/Scar Tissue" |
           injury_2 == "Knee Lateral Capsule Sprain 1 Deg" |
           injury_2 == "Knee Lateral Collateral Sprain" |
           injury_2 == "Knee Lateral Collateral Sprain 2 Dg" |
           injury_2 == "Knee Lateral Hamstring Strain/Distal" |
           injury_2 == "Knee Medial Capsule Sprain" | 
           injury_2 == "Knee Medial Collateral Sprain" | 
           injury_2 == "Knee Medial Collateral Sprain 1 Deg" | 
           injury_2 == "Knee Medial Collateral Sprain 2 Deg" | 
           injury_2 == "Knee Medial Hamstrng Strain/Distal" | 
           injury_2 == "Knee Posterior Cruciate Sprain 3 Dg"| 
           injury_2 == "Knee Posterior-Medial Capsule Sprain" | 
           injury_2 == "Knee Quadriceps Strain/Distal 2 Deg" | 
           injury_2 == "Knee sprain" | 
           injury_2 == "Knee Sprain (non-specific)" | 
           injury_2 == "Knee Tibial Plateau Contusion" |
           injury_2 == "Knee, musculo-skeletal" | 
           injury_2 == "Meniscus Injury" |
           injury_2 == "Meniscus Medial Tear" | 
           injury_2 == "Patella Contusion" | 
           injury_2 == "Patella Dislocation/Acute - Lateral" | 
           injury_2 == "Patella Femoral Syndrome" |
           injury_2 == "Patella Prepatellar Bursa Contusion" |
           injury_2 == "Patella Subluxation/Acute - Lateral" |
           injury_2 == "Patella Subluxation/Acute - Medial" |
           injury_2 == "Patella Tendinitis (Chronic)" | 
           injury_2 == "Thigh Hamstring Strain/Medial Belly" | 
           injury_2 == "Thigh Lateral Contusion" | 
           injury_2 == "Thigh Quads Strain/Belly" | 
           injury_2 == "Thigh Quads Strain/Belly 1 Deg" | 
           injury_2 == "Thigh Rectus Femoris Contusion" |
           injury_2 == "Thigh Rectus Femoris Strain 1 Deg" |
           injury_2 == "Thigh Vastus Medialis Contusion" |
           injury_2 == "Tibia Bony Contusion" |
           injury_2 == "Tibia Bony Contusion Distal" |
           injury_2 == "Tibia Fracture/Distal/Avulsion" |
           injury_2 == "Tibia Medial Stress Syndrome" |
           injury_2 == "Tibia Osgood/Schlatter's Syndrome" |
           injury_2 == "Tibia Shin Splints" |
           injury_2 == "Tibia/shin sprain" |
           injury_2 == "Toe 5th M-P Joint Sprain")
           

#code above filters partiicpants whose second non-concussion injuries occured within one year of concussion

#when code first ran - total was 1137 individuals
#filter individuals days_between_injury >= 0 - total reduced to 1107 individuals
#filter individuals days_between_injury <= 365 - total reduced to 678
#filter individuals with lower extremity injuries to new data frame - total reduced to 238 individuals
# total reduced to 233 when age range restricted to 12-18 

#export sims data with no names

sims_data_1 <- sims_concussion_first_injury_data %>% 
  select(-last_name, -first_name)

sims_data_2 <- sims_concussion_first_injury_le_second_injury %>% 
  select(-last_name, -first_name)

library(writexl)

write_xlsx(sims_data_1, "sims_data_1.xlsx")

write_xlsx(sims_data_2, "sims_data_2.xlsx")


```

```{r, include=FALSE}
#loading up impact data to match post-injury 1 IMPACT scores

files <- dir_ls(here::here("data"), glob = "*.csv")

d <- map_df(files, read_csv, .id = "file",
                 col_types = cols(.default = "c")) %>% 
  modify(~parse_guess(.x)) %>% 
  janitor::clean_names() %>% 
  mutate(year = parse_number(file)) %>% 
  mutate(year = as.factor(year))

d <- d %>% 
  mutate(first_name = str_to_title(first_name),
         last_name = str_to_title(last_name))

impact_variables <- d %>% 
  select(passport_id,
         first_name, 
         last_name, 
         test_type,
         test_date,
         user_memory_composite_score_verbal,
         user_memory_composite_score_visual,
         user_visual_motor_composite_score,
         user_impulse_control_composite_score,
         user_reaction_time_composite_score) %>% 
  rename(verbal_memory = user_memory_composite_score_verbal,
         visual_memory = user_memory_composite_score_visual,
         visual_motor = user_visual_motor_composite_score,
         impulse_control = user_impulse_control_composite_score,
         reaction_time = user_reaction_time_composite_score) %>% 
  filter(test_type == "Post-Injury 1")

str(impact_variables)

impact_variables %>% 
  count(passport_id)

impact_variables$test_date <- as.Date(impact_variables$test_date, format = "%m/%d/%Y")

sims_impact_data <- left_join(sims_concussion_first_injury_data, impact_variables) %>% 
  na.omit() %>% 
  select(-passport_id, -test_type) %>% 
  mutate(days_between_injury_test_date = test_date - onset_1) %>% 
  filter(days_between_injury_test_date >= 0 & days_between_injury_test_date <= 100)

#when data sets first joined, there were 907 total observations - 229 than sims only data set. 
#missing values removed leaving data set with 458 observations
#days between injury 1 onset date filtered to be greater than or equal to 0 days and less than or equal to 100 days leaving 328 observations 

sims_impact_data <- sims_impact_data %>% 
  select(c(1:23, 29, 24:28))

sims_impact_data_all_injuries <- sims_impact_data %>% 
  select(-last_name, -first_name)

write_xlsx(sims_impact_data_all_injuries,"sims_impact_data_all_injuries.xlsx")

sims_impact_data_le_injury_only <- left_join(sims_concussion_first_injury_le_second_injury,
                                             impact_variables) %>% 
  na.omit() %>% 
  select(-passport_id, -test_type) %>% 
  mutate(days_between_injury_test_date = test_date - onset_1) %>% 
  filter(days_between_injury_test_date >= 0 & days_between_injury_test_date <= 100)

write_xlsx(sims_impact_data_le_injury_only, "sims_impact_data_le_injury_only.xlsx")

#with lower injuries only, combined with impact, there are 106 observations - ages filtered to be 12-18

  
```

# Data Background {.tabset .tabset-fade .tabset-pills}

Tables display data from sample 238 individuals from Sims data set that sustained a lower extremity injury within 1 year of sustaining a concussion. To include more data, the information below does not contain information from the merged IMPACT data sample. 

## Gender 

```{r, include=TRUE}
gender_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(gender) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )

```

```{r, include=TRUE}
gender_total_tbl
```

## Age at Concussion

```{r, include=FALSE}
concussion_age_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(age_1) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      age_1 = colDef(name = "Age"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )


```

```{r, include=TRUE}
concussion_age_total_tbl
```

## Age at Second Injury

```{r, include=FALSE}
second_age_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(age_2) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      age_2 = colDef(name = "Age"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )


```

```{r, include=TRUE}
second_age_total_tbl
```

## League

```{r, include=FALSE}
league_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(league) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      league = colDef(name = "League"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
league_total_tbl
```

## School 

```{r, include=FALSE}
school_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(league, school_2) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      league = colDef(name = "League"),
      school_2 = colDef(name = "School"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
school_total_tbl
```

## Sport Played Concussion Injury 

```{r, include=FALSE}
sport_1_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(sport_1) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      sport_1 = colDef(name = "Sport"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
sport_1_total_tbl
```

## Sport Level Concussion Injury 

```{r, include=FALSE}
level_1_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(level_1) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      level_1 = colDef(name = "Level"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
level_1_total_tbl
```

## Sport Played Lower Extremity Injury 

```{r, include=FALSE}
sport_2_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(sport_2) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      sport_2 = colDef(name = "Sport"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
sport_2_total_tbl
```

## Sport Level Lower Extremity Injury 

```{r, include=FALSE}
level_2_total_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(level_2) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      level_2 = colDef(name = "Level"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
level_2_total_tbl
```

# Second Injury Frequency 

Table reflects 238 individuals from Sims data set with a diagnosed lower extremity injury following a concussion. 

```{r, include=FALSE}
head(sims_concussion_first_injury_le_second_injury)

sims_concussion_first_injury_le_second_injury %>% 
  count(injury_2)

injury_2_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(injury_2) %>% 
  summarize(total = n()) %>% 
  reactable(
    columns = list(
      injury_2 = colDef(name = "Injury"),
      total = colDef(name = "Total")),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

```

```{r, include=TRUE}
injury_2_tbl
```

# Duration of Time Between Concussion and Lower Extremity Injury {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
gender_time_between_tbl <- sims_concussion_first_injury_le_second_injury %>% 
  group_by(gender) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>%
  filter(gender == "Female" |
         gender == "Male") %>% 
  mutate(mean = as.numeric(mean),
         sd = as.numeric(sd),
         min = as.numeric(min),
         max = as.numeric(max),
         total = as.numeric(total)) %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )


```

## Gender {.tabset .tabset-fade .tabset-pills}

### Summary Table

Descriptive statistics of time between concussion and lower extremity injury by gender

```{r, include=TRUE}
gender_time_between_tbl
```

### Box Plot

```{r, include=FALSE}
gender_tee <- sims_concussion_first_injury_le_second_injury %>% 
  filter(gender == "Female" |
           gender == "Male")

bxp <- ggboxplot(
  gender_tee, x = "gender", y = "days_between_injury", 
  ylab = "Number of Days", xlab = "Gender", add = "jitter",
  title = "Days Between Injuries"
  )

bxp +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
bxp +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

### *T*-Test Results

```{r, include=FALSE}
gender_tee <- gender_tee %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

gender_tee_results <- gender_tee %>% 
  t_test(days_between_injury ~ gender) %>% 
  add_significance()

gender_tee_results
```

```{r, include=TRUE}
gender_tee_results 
```

## Age {.tabset .tabset-fade .tabset-pills}

### Age Difference Distribution

To create plot, a new variable was created `age_difference` calculated as the difference between injury_2 age and injury_1 age. All differences are less than one year. The distribution is not normal with higher distribution at both tails. 

```{r, include=FALSE}
age_diff <- sims_concussion_first_injury_le_second_injury %>% 
  mutate(age_difference = age_2 - age_1)

hist(age_diff$age_difference)

age_diff_plot <- ggplot(age_diff, aes(age_difference)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  labs(x = "Age Difference (Years)",
       y = "Number of Individuals",
       title = "Age Difference in Years between Two Injuries",
       caption = "All injuries less than one year apart")
```

```{r, include=TRUE}
age_diff_plot
```

### Age 1 Total Distribution

```{r, include=TRUE}
ggplot(age_diff, aes(age_1)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 50) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at First Injury")

```

### Age 1 Distribution League

```{r, include=TRUE}
ggplot(age_diff, aes(age_1)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  facet_wrap(~league) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at First Injury")
```

### Age 1 Distribution Gender

```{r, include=TRUE}
ggplot(age_diff, aes(age_1)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~gender) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at First Injury")
```


### Age 2 Total Distribution

```{r, include=TRUE}
ggplot(age_diff, aes(age_2)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 50) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at Second Injury")

```

### Age 2 Distribution League

```{r, include=TRUE}
ggplot(age_diff, aes(age_2)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  facet_wrap(~league) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at Second Injury")
```

### Age 2 Distribution Gender

```{r, include=TRUE}
ggplot(age_diff, aes(age_2)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 10) +
  facet_wrap(~gender) +
  labs(x = "Age",
       y = "Number of Individuals",
       title = "Age at Second Injury")
```

```{r, include=FALSE}
age_diff <- age_diff %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

age_diff_mod <- lm(days_between_injury ~ age_2, data = age_diff)

summary(age_diff_mod)
```

### Age Model 

To produce the model, I calculated the relationship between the age at second injury and the days between injuries. There appears to be a significant relationship, although the model only accounts for 5% of the variance. Overall, there is a 31.339 unit increase in the days between injury for every unit increase in the age at time of 2nd injury. 

```{r, include=TRUE}
summary(age_diff_mod)
```

## Sport {.tabset .tabset-fade .tabset-pills}

This section primarily explores the time between injuries for Football and Women's Soccer as those are the two most common sports at time of concussion and lower extremity injury. 

### Descriptive Statistics

Table displayed statistics of the number of days between injuries for individuals who sustained their injuries playing football or women's soccer.

```{r, include=FALSE}
sport_time_between <- sims_concussion_first_injury_le_second_injury %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

spt_tbl <- sport_time_between %>% 
  group_by(sport_1, sport_2) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>% 
  reactable(
    columns = list(
      sport_1 = colDef(name = "Sport 1"),
      sport_2 = colDef(name = "Sport 2"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
spt_tbl
```

### Sport 2 Injury Type

Table displays the number of lower extremity injuries for individuals who played football and women's soccer. 

```{r, include=FALSE}
spt_2_tbl <- sport_time_between %>% 
  group_by(sport_2, injury_2) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  reactable(
    columns = list(
      sport_2 = colDef(name = "Sport"),
      injury_2 = colDef(name = "Injury"),
      total = colDef(name = "Total",
                     format = colFormat(suffix = " injuries"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
spt_2_tbl
```

### Box Plot

```{r, include=FALSE}
sport_tee <- sims_concussion_first_injury_le_second_injury %>% 
  filter(sport_1 == "Football" | sport_1 == "Women's Soccer",
         sport_2 == "Football" | sport_2 == "Women's Soccer") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))


sport_bxp <- ggboxplot(
  sport_tee, x = "sport_2", y = "days_between_injury", 
  ylab = "Number of Days", xlab = "Sport", add = "jitter",
  title = "Days Between Injuries"
  )

sport_bxp +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

```{r, include=TRUE}
sport_bxp +
  stat_compare_means(method = "t.test", hjust = -0.2)
```

### *T*-Test Results

```{r, include=FALSE}
sport_tee_results <- sport_tee %>% 
  t_test(days_between_injury ~ sport_2) %>% 
  add_significance()

sport_tee_results
```

```{r, include=TRUE}
sport_tee_results 
```

## School {.tabset .tabset-fade .tabset-pills}

Schools with 20 or more individuals included. 

### Descriptive Statistics 

Table displayed statistics of the number of days between injuries for individuals who attend Kalaheo High School, Maui High School, and Mililani High Schol.

```{r, include=FALSE}
school_analysis <- sims_concussion_first_injury_le_second_injury %>% 
  filter(school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))


school_tbl <- school_analysis %>% 
  group_by(school_2) %>% 
  summarize(mean = mean(days_between_injury),
            sd = sd(days_between_injury),
            min = min(days_between_injury),
            max = max(days_between_injury),
            total = length(days_between_injury)) %>% 
  reactable(
    columns = list(
      school_2 = colDef(name = "School"),
      mean = colDef(name = "Mean",
                    format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      sd = colDef(name = "SD",
                  format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      min = colDef(name = "Min",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      max = colDef(name = "Max",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " days")),
      total = colDef(name = "Total",
                   format = colFormat(digits = 2, separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
school_tbl
```

### Boxplot

```{r, include=FALSE}
school_analysis <- sims_concussion_first_injury_le_second_injury %>% 
  filter(school_2 == "Maui High School" |
           school_2 == "Kalaheo High School" |
           school_2 == "Mililani High School") %>% 
  mutate(days_between_injury = as.numeric(days_between_injury))

sch_plot <- ggboxplot(school_analysis, x = "school_2", y = "days_between_injury", 
          color = "school_2", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          order = c("Maui High School", "Kalaheo High School", "Mililani High School"),
          ylab = "Number of Days", xlab = "", add = "jitter")

```

```{r, include=TRUE}
sch_plot
```

### Anova 

The difference between the mean number of days between injury across the three high schools is significantly different. Students at Mililani High School, on average, experienced a much longer duration of time between injuries than students at Kalaheo High School and Maui High School.

```{r, include=FALSE}
school_res_aov <- aov(days_between_injury ~ school_2, data = school_analysis)

summary(school_res_aov)
```

```{r, include=TRUE}
summary(school_res_aov)

```